Adaptive Shrinkage Illustration

### 2015-10-06 examples/adaptive_shrinkage.rmd
finish refining discussion and implementation

@@

Let's see how these are affected by changing the modelling assumptions so that
the standardized beta are exchangeable (rather than the beta being exchangeable).
```{r run-ash-ES}
beta.bignormal.ash.ES = ash(sim.bignormal$input$betahat, s,model="ES",mixcompdist="normal")
beta.spiky.ash.ES = ash(sim.spiky$input$betahat, s,model="ES",mixcompdist="normal")
df.ES = make_df_for_ashplot(sim.spiky,sim.bignormal,beta.spiky.ash.ES,beta.bignormal.ash.ES)
ashplot(df.ES,ylab="Shrunken beta estimate (ES model)")
pval_plot(df.ES)
```

>>>>

Now plot lfsr against z scores, colored
according to the (square root of) precision

```{r plotting lfsr}

z_lfsr_plot=function(df,ylab="Observed Z score",xlab="lfsr"){
  ggplot(df,aes(x=lfsr,y=betahat/s,color=1/s)) + 
    xlab(xlab) +
    ylab(ylab) + geom_point() +  facet_grid(.~scenario) + scale_colour_gradient2(midpoint = median(1/s),low="blue", mid="white",high="red",space="Lab") 
}

z_lfsr_plot(df)
ggsave("z_vs_lfsr.pdf")
```

@@

Let's see how these are affected by changing the modelling assumptions so that
the standardized beta are exchangeable (rather than the beta being exchangeable).
```{r run-ash-ET}
beta.bignormal.ash.ET = ash(sim.bignormal$input$betahat, s,model="ET",mixcompdist="normal")
beta.spiky.ash.ET = ash(sim.spiky$input$betahat, s,model="ET",mixcompdist="normal")
df.ET = make_df_for_ashplot(sim.spiky,sim.bignormal,beta.spiky.ash.ET,beta.bignormal.ash.ET)
ashplot(df.ET,ylab="Shrunken beta estimate (ET model)")
pval_plot(df.ET)
```
